---
title: "STL Lead Inequity"
format: html
editor: visual
---

### Load libraries 

```{r}
library(tidyverse)
library(janitor)

```

### Read data 

```{r}
stl_lead <- read_csv(here::here("data","stl_blood_lead.csv")) %>% 
  clean_names()
  

```

### Create new data frame with added column- proportion of each census tract that is white

```{r}
stl_lead_prop <- mutate(stl_lead, prop_white = ((white / total_pop) * 100)) 

```

### Plot pct. elevated lead level and prop_white

```{r}
stl_lead_plot <- ggplot(data = stl_lead_prop, aes(x = pct_elevated, y = prop_white)) + 
  geom_point(size = 2, 
             color = "red",
             alpha = 0.5) +
  xlab("Percentage of children with elevated blood lead levels") + 
  ylab("Proportion of census tract that is white (%)") + 
  theme_minimal() 

stl_lead_plot

```

### Saving plot 

```{r}
ggsave(here::here("figs","stl_lead_plot.png"),
       width = 6,
       height = 5)
```

There is a general trend of areas with a higher proportion of the population identifying as "white", there is a lower percentage of children with elevated blood lead levels.

### Creating a histogram 

```{r}
stl_lead_histogram <- ggplot(data = stl_lead_prop, aes(x = pct_elevated)) + 
  geom_histogram(color = "dodgerblue3", 
                 fill = "dodgerblue") + 
  xlab("Percent of children with elevated blood lead level") + 
  ylab("Number of census tracts") + 
  theme_minimal()

stl_lead_histogram
```

### Export histogram 

```{r}
ggsave(here::here("figs","stl_lead_histogram.png"), 
       width = 6, 
       height = 5)
```
